\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-12-06 main.Rmd
small tweak on section heading in examples, fix x axis label

Forming a cubble + basic tidyverse verbs - Vig 2 Aggregation - Vig 4

@@

### Spatial manipulation

@@

### Temporal manipulation

@@

### Back to spatial

@@

## Spatial and temporal aggregation

@@

### Hierarchical data structure

@@

## Matching precipitation and river level in Victria water gauges

@@

### Theory

@@

### Rainfall translates into river level

@@

## Spatio-temporal data with NetCDF

```{r}
nc <- ncdf4::nc_open(here::here("data/adaptor.mars.internal-1638344933.932894-4194-11-a5d35ac3-b36d-4982-afa5-a5dd193a6718.nc"))
temp <- as_cubble(nc, vars = "d2m")
vic_map <- ozmaps::abs_ste %>% filter(NAME == "Victoria")

>>>>

@@

@@

@@

@@

### Aggregation

@@

@@

## River level data in Victria water gauges

@@

@@

@@

## ERA5: climate reanalysis data

```{r eval = FALSE}
nc <- ncdf4::nc_open(here::here("data/adaptor.mars.internal-1638344933.932894-4194-11-a5d35ac3-b36d-4982-afa5-a5dd193a6718.nc"))

nc <- ncdf4::nc_open(here::here("data/tas_Amon_ACCESS-CM2_ssp585_r1i1p1f1_gn_20150116-20201216_v20191108.nc"))
temp <- as_cubble(nc, vars = "tas")
vic_map <- ozmaps::abs_ste %>% filter(NAME == "Victoria")

### 2021-12-06 main.tex
small tweak on section heading in examples, fix x axis label

\hypertarget{spatial-manipulation}{%
\subsubsection{Spatial manipulation}\label{spatial-manipulation}}

@@

\hypertarget{temporal-manipulation}{%
\subsubsection{Temporal manipulation}\label{temporal-manipulation}}

@@

\hypertarget{back-to-spatial}{%
\subsubsection{Back to spatial}\label{back-to-spatial}}

@@

\hypertarget{spatial-and-temporal-aggregation}{%
\subsection{Spatial and temporal
aggregation}\label{spatial-and-temporal-aggregation}}

@@

\hypertarget{hierarchical-data-structure}{%
\subsubsection{Hierarchical data
structure}\label{hierarchical-data-structure}}

@@

\hypertarget{matching-precipitation-and-river-level-in-victria-water-gauges}{%
\subsection{Matching precipitation and river level in Victria water
gauges}\label{matching-precipitation-and-river-level-in-victria-water-gauges}}

@@

\hypertarget{theory}{%
\subsubsection{Theory}\label{theory}}

@@

\hypertarget{rainfall-translates-into-river-level}{%
\subsubsection{Rainfall translates into river
level}\label{rainfall-translates-into-river-level}}

@@

\hypertarget{spatio-temporal-data-with-netcdf}{%
\subsection{Spatio-temporal data with
NetCDF}\label{spatio-temporal-data-with-netcdf}}

\begin{CodeChunk}
\begin{CodeInput}
R> nc <- ncdf4::nc_open(here::here("data/adaptor.mars.internal-1638344933.932894-4194-11-a5d35ac3-b36d-4982-afa5-a5dd193a6718.nc"))
R> temp <- as_cubble(nc, vars = "d2m")
R> vic_map <- ozmaps::abs_ste %>% filter(NAME == "Victoria")
R> 
R> res <- temp %>% 
+   stretch(ts) %>% 
+   mutate(d2m = d2m - 273.15) %>% 
+   filter(lubridate::hour(time) == 12) %>% 
+   group_by(id) %>% 
+   summarise(d2m = mean(d2m, na.rm= TRUE)) %>%
+   migrate(long, lat)
R> 
R> vic_string <- vic_map %>% sf::st_cast("MULTILINESTRING") 
R> 
R> res %>% 
+   ggplot() +
+   geom_tile(aes(x = long, y = lat, fill = d2m)) +
+   geom_sf(data = vic_string , alpha = 0.5, fill = "transparent") +
+   theme_bw() + 
+   colorspace::scale_fill_continuous_sequential("Mint")
\end{CodeInput}

\begin{center}\includegraphics{figures/unnamed-chunk-23-1} \end{center}

>>>>

@@

@@

@@

\hypertarget{aggregation}{%
\subsubsection{Aggregation}\label{aggregation}}

@@

@@

\hypertarget{river-level-data-in-victria-water-gauges}{%
\subsection{River level data in Victria water
gauges}\label{river-level-data-in-victria-water-gauges}}

@@

@@

@@

\hypertarget{era5-climate-reanalysis-data}{%
\subsection{ERA5: climate reanalysis
data}\label{era5-climate-reanalysis-data}}

\begin{CodeChunk}
\begin{CodeInput}
R> nc <- ncdf4::nc_open(here::here("data/adaptor.mars.internal-1638344933.932894-4194-11-a5d35ac3-b36d-4982-afa5-a5dd193a6718.nc"))
R> 
R> nc <- ncdf4::nc_open(here::here("data/tas_Amon_ACCESS-CM2_ssp585_r1i1p1f1_gn_20150116-20201216_v20191108.nc"))
R> temp <- as_cubble(nc, vars = "tas")
R> vic_map <- ozmaps::abs_ste %>% filter(NAME == "Victoria")
R> 
R> res <- temp %>% 
+   stretch(ts) %>% 
+   mutate(d2m = d2m - 273.15) %>% 
+   filter(lubridate::hour(time) == 12) %>% 
+   group_by(id) %>% 
+   summarise(d2m = mean(d2m, na.rm= TRUE)) %>%
+   migrate(long, lat)
R> 
R> vic_string <- vic_map %>% sf::st_cast("MULTILINESTRING") 
R> 
R> res %>% 
+   ggplot() +
+   geom_tile(aes(x = long, y = lat, fill = d2m)) +
+   geom_sf(data = vic_string , alpha = 0.5, fill = "transparent") +
+   theme_bw() + 
+   colorspace::scale_fill_continuous_sequential("Mint")
\end{CodeInput}
\end{CodeChunk}
